% This file makes a web version of the blueprint It should include all the
% \usepackage needed for this version. The template includes standard AMS
% packages. It is otherwise a very minimal preamble (you should probably at
% least add cleveref and tikz-cd).

\documentclass{report}

\usepackage{amssymb, amsthm, amsmath}
\usepackage{hyperref}
\usepackage[showmore, dep_graph]{blueprint}

\input{macros/common}
\input{macros/web}

\home{https://vbeffara.github.io/Cours_ED}
\github{https://github.com/vbeffara/Cours_ED}
\dochome{https://vbeffara.github.io/Cours_ED/docs}

\title{Introduction to proof assistants}
\author{VB and the course participants}

\begin{document}
\maketitle

\section*{Installing Lean on your computer}

The whole system is rather heavy on resources, but installing it should be
straightforward. Ensure that you have a fast connection before starting. Here is
what I advise you to do:
\begin{enumerate}
  \item Collaboration will be \textbf{a lot} smoother if you have a github
    account with an SSH key activated, details of how to do this depend on your
    system (and it is not strictly necessary). If you do, tell me what your
    github name is so that I can add you to the project.
  \item Install VSCode, available at \url{https://code.visualstudio.com/}.
  \item Within VSCode, install the \texttt{Lean 4} extension.
  \item There should be a $\forall$-shaped button appearing in the top-right
    corner, click it and choose ``Open Project...'' then ``Download project...''
    and enter the course URL in the dialog: either
    \url{git@github.com:vbeffara/Cours_ED.git} if you did step 1, or
    \url{https://github.com/vbeffara/Cours_ED.git} if you didn't. This will
    download the project to a folder you will choose on your computer.
  \item VSCode will proceed to install all the necessary pieces for you, after
    asking for confirmation. (It is possible to install the system by hand, but
    it is a little involved if you want all the bells and whistles like
    pre-built libraries and everything, see here:
    \url{https://leanprover-community.github.io/get_started.html}.)
  \item Choose to open the newly created project in VSCode.
  \item That's it, you should now have a functional Lean system.
\end{enumerate}

\input{content}
\end{document}